problem years

### 2024-08-14 src/problem_years.Rmd
gini

@@

>>>>

### Gini

```{r}

# No need to add 0s like OAs as there aren't any LA with 0s

gini.df <- data.frame()

for (t in 1996:2012){
    a <- df %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/gini/gini_la.csv")
gini.df %>% write_csv(path.out)
```

@@

### Gini

```{r}

# No need to add 0s like OAs as there aren't any LA with 0s

gini.df <- data.frame()

for (t in 1996:2012){
    a <- df %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/gini/gini_oa.csv")
gini.df %>% write_csv(path.out)
```

### 2024-08-14 src/problem_years_10.Rmd
gini

@@

>>>>

### Gini

```{r}

# No need to add 0s like OAs as there aren't any LA with 0s

gini.df <- data.frame()

for (t in 1996:2012){
    a <- df %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/gini/gini_la_10.csv")
gini.df %>% write_csv(path.out)
```

@@

### Gini

```{r}

# No need to add 0s like OAs as there aren't any LA with 0s

gini.df <- data.frame()

for (t in 1996:2012){
    a <- df %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/gini/gini_oa_10.csv")
gini.df %>% write_csv(path.out)
```
